Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-22 sections/eval.tex
Update on Overleaf.

\subsection{Implementing Numpy's Array API in Finch}
In the past decade, the adoption of the Numpy Array API \cite{harris_array_2020} has allowed for a proliferation array programming systems, but existing implementations of this API for structured data suffer from either incompleteness or inefficiency. They generally either limit the dimensionality to vectors and matrices or only support tabular representations in order to reduce the complexity of interactions between different formats. Further, existing work doesn't support the fusion of arbitrary operators which can have a drastic impact on performance as we show in Fig. (\kyle{PUT FIG HERE}). We believe that a flexible, online compiler like Finch which can manage the complexity of arbitrary operations between inputs with a wide variety of formats is the secret ingredient needed to make the array API performant for structured data.

@@

\subsubsection{The Finch High-Level API (Needs a Name)}

>>>>

\subsection{Implementing Numpy's Array API in Finch}
In the past decade, the adoption of the Python Array API \cite{harris_array_2020} has allowed for a proliferation array programming systems, but existing implementations of this API for structured data suffer from either incompleteness or inefficiency. They generally either limit the dimensionality to vectors and matrices or only support tabular representations in order to reduce the complexity of interactions between different formats. Further, existing work doesn't support the fusion of arbitrary operators which can have a drastic impact on performance as we show in Fig. (\kyle{PUT FIG HERE}). We believe that a flexible, online compiler like Finch which can manage the complexity of arbitrary operations between inputs with a wide variety of formats is the secret ingredient needed to make the array API performant for structured data.

@@

To get a sense of the Python Array API, we provide a few examples of their
